---
title: "Time Series Analysis, Case 6"
author: "Andew, Carmen, Jimmy, Naresh"
date: "23 January 2016"
output: html_document
---

We are going to analyze six simulated time series, and in all of them we have to decide,
in a visual and graphical way, if they are or not Covariance-Stationary (CS), White Noise
(WN), Strict White Noise (SWN) or Gaussian White Noise (GWN). We will also analyze
the real time series for the daily Brent Dated spot prices and its corresponding returns.

```{r,echo=FALSE}
setwd("/home/ab/Documents/MBD/time_series/case6")
```

First, we load the two datasets
```{r}
real = read.csv("Session6real.csv", sep = "",dec = ",")
names(real) = "price"
sim = read.csv("Session6sim.csv", sep = ";",dec = ",")
```


##Analysis of the Real Data
We need to add a difference value that look at the difference between the price and the previous day. To do this we create a lag of t-1 and then calculate the different.
```{r}
real$lag = lag(real$price,1)
real$diff = real$price - real$lag
ts.plot(real$diff)
```


###Step 1. Plot the series and compute basic statistics
First we compute the mean, standard deviation and the variance of the time series. We then plot the series and see the data is not stationary. The variance is different across the time series so can assume it is not stationary (is this right guys?). 
```{r}
summary(real$price)
sd(real$price)
var(real$price)
ts.plot(real$price, main = "Time Series Plot of Daily Brent Spot Prices ($/bbl)")
ts.plot(real$diff, main = "Time Series Plot of Difference in Daily Brent Spot Prices ($/bbl)")
```

###Step 2. Plot the acf and pacf for the series
We now plot the Auto Correlation Function and the Partial AutoCorrelation Function
```{r}
acf(real$price, main = "Auto Correlation Function Plot of Daily Brent Spot Prices ($/bbl)")
acf(real$price,type = "partial", main = "Partial Auto Correlation Function Plot of Daily Brent Spot Prices ($/bbl)")
names(real)
acf(real$price, main = "Auto Correlation Function Plot of Difference Daily Brent Spot Prices ($/bbl)")
acf(real$price,type = "partial", main = "Partial Auto Correlation Function Plot of Difference Daily Brent Spot Prices ($/bbl)")
```


###Step 3. Test Normality

1. A stochastic process is covariance stationary (or weak stationary) if
  a. E(Yt) = µ, for all t
  b. Var(Yt) = σy2, for all t
  c. Cov(Yt,Yt-h) = ϒ(h), for all t and h
2. A process is white noise if it is
  a. Covariance Stationary
  b. Uncorrelated
  c. Zero mean
3. A process is strict white noise if it is
  a. Covariance Stationary
  b. Zero mean
  c. Independent and identically distributed (iid)

ts.plot(log(real), main = "Time Series Plot of Daily Brent Spot Prices ($/bbl)")

